### 2015-12-05 paper/4-performance.tex
Add system specs.
Update profiling call-graphs.

%TODO say that you will now prove your claims about the aproach having nearly no impact
%TODO and potentially even claim that you are faster than adevs for some situations, due to the algorithms from PythonPDEVS and further features
%TODO briefly give some hardware info on the machine (CPU, OS, RAM), used software (version of adevs, GCC, ...), and about number of samples/variance
\subsection{Sequential Simulation}
%TODO we start with sequential simulation results, because this is still base case
%TODO compare CPU time with adevs for some benchmarks
%TODO and explain why there is such a difference
%TODO (spend some time here, as this is also important)
%\subsubsection{CPU Usage}
%TODO !!! benchmarks are in integers
The benchmark models are identical in functionality (between adevs/dxex versions). Dxex uses integer timestamps, adevs can only use floating point (of the same values).
\subsubsection{Devstone}
The Devstone \cite{DEVStone} benchmark is highly hierarchical, using Direct connection the dxex kernels can exploit this, whereas adevs needs to walk the structure of the model to pass events.\\
\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig1.eps}
	\label{fig1.eps}
\end{figure}

>>>>

%TODO say that you will now prove your claims about the aproach having nearly no impact
%TODO and potentially even claim that you are faster than adevs for some situations, due to the algorithms from PythonPDEVS and further features
%TODO briefly give some hardware info on the machine (CPU, OS, RAM), used software (version of adevs, GCC, ...), and about number of samples/variance
\subsection{Sequential Simulation}
%TODO we start with sequential simulation results, because this is still base case
%TODO compare CPU time with adevs for some benchmarks
%TODO and explain why there is such a difference
%TODO (spend some time here, as this is also important)
\subsection{Preamble}
The benchmark models are identical in functionality (between adevs/dxex versions). Dxex uses integer timestamps, adevs uses floating point. Tests show there is little difference performance wise (both types fit in a machine word)\\
Benchmarks ran on a i7-2670QM, 16GiB Ram, Arch Linux (4.2.5 kernel). Analysis of the benchmark results is done using call-graphs generated by perf, a selection of those call-graphs can be found in the code repository.
\subsubsection{Devstone}
The Devstone \cite{DEVStone} benchmark is highly hierarchical, using Direct connection the dxex kernels can exploit this, whereas adevs needs to walk the structure of the model to pass events.\\
\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig1.eps}
	\label{fig1.eps}
\end{figure}
